Agile Inter-team Software Development

### 2019-01-20 Draft/Parts/Main.tex
Changed files to use one line per sentence (better change tracking).
Added content from Spotify reference.

@@

\section{Importance of Architecture/Design}
\label{sec:imp_of_dsgn}
As we know that the product owner in an agile process model is the person with the vision of what the project will look like and if it is a small team the product owner can clearly pass this to each and every member of the team and even each member can query the product owner directly when in doubt. But in large scale projects where multiple agile teams are working together in supervision of a few product owners it is practically impossible for the owner to keep doing what they did in a small team, that’s where a formal definition of their vision comes in handy as it enables the teams to look up to something when encountering a design decision. The design or architecture in this case acts as a common vision for not only the teams but also for the communication between all the product owners. The design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} as when the teams can’t come to a common consensus the design shows the path to take.

>>>>

\section{NAME ME} 
For a typical example of a company using many agile teams, consider Spotify who has over 30 teams \cite{kniberg12}.
The basic element of the development organization at Spotify is the Squad, analgous to a Scrum team.
Each Squad is the autonomous developer, with a localized working area, of a particular sub-system in the product.
Squads in related areas are grouped together into Tribes.
Although larger than Squads (7-10 members), Tribes are limited in size (< 100) to ensure smooth communication.

%add image

\subsection{NAME ME}
%social fixes
A fundamental issue with tasking teams with different goals is that teams can become isolated with respect to the context of their work.
At Spotify \cite{kniberg12}, offices are laid out so that the Squads making up a Tribe are spatially close. This leads to an environment where an informal exchange of information on the Tribes work will occur.
%second problem
Consider another secnario: a tester on a particular agile team invests time to solve a particular problem, which is also faced by another tester on a different team. Without communication, these team members would perform redundant work.
To address this problem Spotify defines Chapters \cite{kniberg12}, which are crosscutting divisions which gathers inviduals with simular roles accross different Squads.

@@

\section{Importance of Architecture/Design}\label{sec:imp_of_dsgn}
%Why is Design/Architecture so important when doing this?

As we know that the product owner in an agile process model is the person with the vision of what the project will look like and if it is a small team the product owner can clearly pass this to each and every member of the team and even each member can query the product owner directly when in doubt.
But in large scale projects where multiple agile teams are working together in supervision of a few product owners it is practically impossible for the owner to keep doing what they did in a small team, that’s where a formal definition of their vision comes in handy as it enables the teams to look up to something when encountering a design decision.
The design or architecture in this case acts as a common vision for not only the teams but also for the communication between all the product owners.
The design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} as when the teams can’t come to a common consensus the design shows the path to take.
%non specification fix
Spotify addresses this issue with a more organizational approach by defining a "system owner" role \cite{kniberg12}.
This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain long term stewardship over a sub-system.
